A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-12-08 paper/MSDS7330DBMSforGeospatiallyEnabledGame - Copy.tex
Rene's draft
Changes to formatting in middle layer section.

Player Registration: Record user profile data (UserID, name, email address) from the client’s input on the mobile device. 
@app.route('/api/game/user)
Input JSON format example: {"userid" : "user01", "firstname" : "Arturo"}

Player State Synchronization: Based on UserID, provide user data through a response to the client from the database.
@app.route('/api/game/user/<userid>')
Input : UserID
Response JSON format : {"userid" : "user01", "firstname" : "Arturo"}

Player location: Instantaneously collect the player’s location data (latitude and longitude coordinates), and update this information in the database when the player moves according to the set thresholds (one update every XX)
@app.route('/api/game/location‘)
Input JSON format example: {"latitude":  "32.7877", "longitude" : " -96.8062"}

List of Objects around the player’s location: Send a response to the client reporting all objects avaialbe for collection, based on current position within a specified radius.
@app.route('/api/game/getlist/<userid>/<r>)
Input : UserID and Radius
Reponse JSON format : List of all available objects

Colission report: Send a response to the client reporting the game score and revealing new story segments, which are triggered according to the SegmentThreshold parameter in the database. 
@app.route('/api/game/collection-reg‘)
Response JSON format : Current Score and Story Segment and story based on score

User score status per Game category API - @app.route('/api/game/user-score/<userid>‘)
Input : UserID
Response JSON format : ScoreCategory and Current score

>>>>

\textbf{Player Registration:} Record user profile data (UserID, name, email address) from the client’s input on the mobile device. 
\textit{Details:}
@app.route('/api/game/user)
Input JSON format example: \big\{"userid" : "user01", "firstname" : "Arturo"\big\}

\textbf{Player State Synchronization:} Based on UserID, provide user data through a response to the client from the database.
\textit{Details:}
@app.route('/api/game/user/<userid>')
Input : UserID
Response JSON format : \big\{"userid" : "user01", "firstname" : "Arturo"\big\}

\textbf{Player location:} Instantaneously collect the player’s location data (latitude and longitude coordinates), and update this information in the database when the player moves according to the set thresholds (one update every XX).
\textit{Details:}
@app.route('/api/game/location‘)
Input JSON format example: \big\{"latitude":  "32.7877", "longitude" : " -96.8062"\big\}

\textbf{List of Objects around the player’s location:} Send a response to the client reporting all objects avaialbe for collection, based on current position within a specified radius.
\textit{Details:}
@app.route('/api/game/getlist/<userid>/<r>)
Input : UserID and Radius
Reponse JSON format : List of all available objects

\textbf{Colission report:} Send a response to the client reporting the game score and revealing new story segments, which are triggered according to the SegmentThreshold parameter in the database. 
\textit{Details:}
@app.route('/api/game/collection-reg‘)
Response JSON format : Current Score and Story Segment and story based on score

\textbf{User score status per Game category:} 
\textit{Details:}
API - @app.route('/api/game/user-score/<userid>‘)
Input : UserID
Response JSON format : ScoreCategory and Current score
